Stochastic Variance-Reduced Policy Gradient

### 2018-02-07 svrpg.tex

In all the experiments we compete with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPG mini-batch size.
The neural network and the learning rate are the same for GPOMDP and SVRPG.
In SVRPG we used two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
We used the stopping condition defined in Section \ref{sec:stopping}.
We fixed the maximum number of trajectories that both the algorithms can use as shown in appendices.

The neural networks is composed of one layer with 8 neurons for Cart-Pole environment and by two layers with 32x32 neurons for Swimmer and for Half Cheetah environments. In each experiment, the length of episodes is 500 steps.

In particular in our experiments we use this technique in the context of G(PO)MDP defined as "weighted per-decision importance sampling estimator" \cite{precup2000eligibility}.

>>>>

\begin{figure}[t]
    \includegraphics[width=0.5\textwidth]{swimmer_self_normalized_SVRPG_vs_GPOMDP}
    \caption{Self-Normalized SVRPG vs GPOMDP in swimmer}
    \label{fig:swimmerone}
\end{figure}
\begin{figure}[t]
    \includegraphics[width=0.5\textwidth]{swimmer_self_normalized_SVRPG_vs_SVRPG}
    \caption{Self-Normalized SVRPG vs Non Self-Normalized SVRPG in swimmer}
    \label{fig:swimmertwo}
\end{figure}
\begin{figure}[t]
    \includegraphics[width=0.5\textwidth]{half_cheetah_self_norm_baseline_SVRPG_vs_GPOMDP100_baseline}
    \caption{Self-Normalized SVRPG with baseline vs GPOMDP with baseline in half cheetah}
    \label{fig:halfcheetah}
\end{figure}
\begin{figure}[t]
    \includegraphics[width=0.5\textwidth]{cart_pole_SVRPG_vs_GPOMDP}
    \caption{SVRPG vs GPOMDP in cart-pole}
    \label{fig:cartpole}
\end{figure}
